---
title: "P2 Processing"
author: "Skip Potts"
date: "Due 3/9/2021"
output: html_document
---
# formatting data and summary stats
```{r}
P2<-cbind(prac_data, price) #joining data sets
P2$job<-factor(P2$job)  #converting factor variables into factors
P2$marital<-factor(P2$marital)
P2$education<-factor(P2$education)
P2$default<-factor(P2$default)
P2$housing<-factor(P2$housing)
P2$loan<-factor(P2$loan)
P2$contact<-factor(P2$contact)
P2$month<-factor(P2$month)
P2$poutcome<-factor(P2$poutcome)
P2$y<-factor(P2$y)
#factors above have blanks counted as a level instead of being NA

P2y.n<-split(P2, P2$y)  #splitting the data into yes and no responses
P2y.n  
summary(P2y.n$no) # summary of no responses (for Table 2)
summary(P2y.n$ye) # summary of yes responses (for Table 2)
summary(P2)  # summary of total responses (for Table 2)
nrow(P2y.n$ye)  #total yes
nrow(P2y.n$no)   #total no
New.P2<-na.omit(P2)  #dataset with no NA's
nrow(New.P2) #data with no NA's, remembering factors are blanks and not NA
```
# Figure 1
```{r}
P2.obs2<-c(59, 20, 29, 55, 2, 65)  #percent levels in table 2 data
P2.obs1<-c(14, 2, 83, 5.6, 44, 36) #percent levels in table 1 data


# plot showing #percent levels in table 1 data vx table 2
plot(P2.obs1,P2.obs2,type="n",xlab="Initial Population by %",ylab="Random Sample by %", xlim=c(-10,90), ylim=c(-10,90))
lines(-10:100,-10:100)
text(P2.obs1,P2.obs2, c("Marital", "Blue Collar", "College", "Mortgage", "Default", "Cell Phone"))
```

# Looking at data
```{r}
#clearing unneeded variables attached to our contact that have many missing values
drop<-c("duration", "previous", "pdays", "campaign", "poutcome") #tracking our work, not necessarily relevant to our purposes.
P2.new<-P2[,!(names(P2) %in% drop)]

nrow(New.P2)/nrow(P2) #percent of data without NAs
summary(P2.new) #age and balance, only missing values according to summary
table(P2$job) #3048 blank, 261 unknown
table(P2$marital) #1108 blank
table(P2$education) #1014 blank, 1816 unknown
table(P2$default) #1929 blank
table(P2$housing) #900 blank
table(P2$loan) #466 blank
#table(P2$poutcome) #removed, not part of final dataset
table(P2$y) #Complete
```



# Data imputation
```{r}
#Analysis of missing data
md.pattern(P.2, rotate.names = TRUE)

# Predictive mean matching, notes below
Practicum_Mice <- mice(P.2,m=5,maxit=50,meth=c("pmm","","","","", "","pmm","","","","","",""),seed=500)
#conduct imputation with PMM method for variables (the variables with no missing values have no method provided)  
#https://stats.idre.ucla.edu/r/faq/how-do-i-perform-multiple-imputation-using-predictive-mean-matching-in-r/
#^^^details on method used in mice for age.  Poission dist used for balance.
#methods(mice)

#Not necessary to write about
Practicum_Mice$meth #display the methods corresponding to each variable
```

# Viewing imputed data
```{r}
Practicum_Mice$imp$age #display 2568 imputed ages for five imputed datasets

#Maybe use?  Data set is so big that we can't see a ton here - maybe just use the density plots below
stripplot(Practicum_Mice, pch = 20, cex = 1)[1:2] #inspect the distribution of original and imputed data
str(Practicum_Mice)

#density plots of dataset against imputed sets for age
P2.age.full <-P.2$age[!is.na(P.2$age)] #use the original begin_weight values with all missing values removed as the raw dataset for comparison with the five imputed datasets
plot(density(P2.age.full), ylim = c(0, 0.05), main = "", xlab = "age", lwd=2)
lines(density(Practicum_Mice$imp$age[,1]), col = "red", lwd=2)
lines(density(Practicum_Mice$imp$age[,2]), col = "blue", lwd=2)
lines(density(Practicum_Mice$imp$age[,3]), col = "green", lwd=2)
lines(density(Practicum_Mice$imp$age[,4]), col = "yellow", lwd=2)
lines(density(Practicum_Mice$imp$age[,5]), col = "orange", lwd=2)
legend("topright", c("raw data", "imputation 1", "imputation 2", "imputation 3", "imputation 4", "imputation 5"), lwd=c(2,2), col=c("black", "red", "blue", "green", "yellow", "orange"))

#density plots of dataset against imputed sets for age
P2.b.full <-P.2$balance[!is.na(P.2$balance)] #use the original begin_weight values with all missing values removed as the raw dataset for comparison with the five imputed datasets
plot(density(P2.b.full), ylim = c(0, 0.0015), xlim = c(0, 4000), main = "", xlab = "age", lwd=2)
lines(density(Practicum_Mice$imp$balance[,1]), col = "red", lwd=2)
lines(density(Practicum_Mice$imp$balance[,2]), col = "blue", lwd=2)
lines(density(Practicum_Mice$imp$balance[,3]), col = "green", lwd=2)
lines(density(Practicum_Mice$imp$balance[,4]), col = "yellow", lwd=2)
lines(density(Practicum_Mice$imp$balance[,5]), col = "orange", lwd=2)
legend("topright", c("raw data", "imputation 1", "imputation 2", "imputation 3", "imputation 4", "imputation 5"), lwd=c(2,2), col=c("black", "red", "blue", "green", "yellow", "orange"))
```
# Chose imputed set 4
```{r}
P.2.mice = complete(Practicum_Mice,4) #creating imputed data set
```


# Checking proportions of yes/no in blanks against full set
```{r}
summary(P.2.mice) 
summary(P2)

P2job<-split(P2, P2$job) #splitting data by job factor level
P2.miss.job<-P2job[[1]] #looking at blank level
summary(P2.miss.job)  #finding missing data y/n ratio
summary(P2) # finding population y/n ratio
x<-360/(2688+360) #y/n same as total pop - MAR 11.8
prop.test(x=c(360,5289), n=c(2688+360, 45211),
          conf.level=0.95)

P2.unk.job<-P2job$unknown  #looking at unknown level
summary(P2.unk.job)
x<-32/(229+32) #y/n close to total pop - MAR 12.2
prop.test(x=c(32,5289), n=c(229+32, 45211),
          conf.level=0.95)

P2mar<-split(P2, P2$marital) #splitting data by marital factor level
P2.miss.m<-P2mar[[1]]
summary(P2.miss.m)
x=148/(148+960) #y/n slightly higher, but close to total pop 13.4
prop.test(x=c(148,5289), n=c(148+960, 45211),
          conf.level=0.95)

P2ed<-split(P2, P2$education) #splitting data by education factor level
P2.miss.e<-P2ed[[1]]  #missing
summary(P2.miss.e)
x=115/(115+899) #y/n same as pop basically - 11.3
prop.test(x=c(115,5289), n=c(115+899, 45211),
          conf.level=0.95)

P2.unk.e<-P2ed$unknown  #unknown  EDUCATION UNKNOWN IS SIGNIFICANTLY DIFFERENT
#but not hugely so
summary(P2.unk.e)
(x=250/(250+1566)) #y/n same as pop basically - 13.8
prop.test(x=c(250,5289), n=c(250+1566, 45211),
          conf.level=0.95)

P2d<-split(P2, P2$default)  #splitting data by default factor level
P2.miss.d<-P2d[[1]]
summary(P2.miss.d)
x=224/(224+1705) #y/n same as pop basically - 11.6
prop.test(x=c(224,5289), n=c(224+1705, 45211),
          conf.level=0.95)

P2h<-split(P2, P2$housing)  #splitting data by housing factor level
P2.miss.h<-P2h[[1]]
summary(P2.miss.h)
x=97/(97+803) #y/n slightly lower, but close to total pop 10.7
prop.test(x=c(97,5289), n=c(97+803, 45211),
          conf.level=0.95)

P2c<-split(P2, P2$contact)  #splitting data by contact factor level
P2.miss.c<-P2c[[1]]
summary(P2.miss.c)
x=6/(6+31) #y/n slightly higher, but close to total pop 16.2 w/very small sample.
#this should be a random recording error likely
prop.test(x=c(6,5289), n=c(37, 45211),
          conf.level=0.95)

P2.unk.c<-P2c$unknown  #Contact type UNKNOWN SIGNIFICANTLY DIFF
summary(P2.unk.c)
(x=530/(530+12478)) #y/n not close to total pop - 4.1 
prop.test(x=c(530,5289), n=c(530+12478, 45211),
          conf.level=0.95)
```
#There is no evidence that MOST missing values come from different distributions.
There is evidence that "unknown" as an education level is statistically different, but not meaningfully so.
There is very strong evidence that contact method unknown is different.  

# Imputing final data set
```{r}
P2.final<-P.2.mice[,!(names(P.2.mice) %in% drop)]
```

# contingency table of conact to check factor level distributions and significant difference from normal pop.
```{r}
xtabs( ~ y + contact, P2.final)
#NA - 16.2%
6/(31+6)
#Unknown - 4.1%
530/(530+12478)
#tele - 13.3%
389/(389+2515)
#cell - 14.9%
4364/(4364+24898)

#prop.test to see if cell is sig diff.
prop.test(x=c(4364,5289), n=c(12478+4364, 45211),
          conf.level=0.95)
#prop.test to see if tele is sig diff.
prop.test(x=c(389,5289), n=c(389+2515, 45211),
          conf.level=0.95)
```
#^^^ Every factor level of contact is significantly different from the standard pop.  
So weird.  Basically, unknown is the biggest issue and it is totally different from tele and cell.  

```{r}
drop<-c("day", "month", "poutcome") #tracking our work, not necessarily relevant to our purposes.
P2.final<-P.2.mice[,!(names(P.2.mice) %in% drop)]
summary(P2.final)
```
# Export final data set
```{r}
write.csv(P2.final,"C:/Users/skip/OneDrive/Desktop/Spring 21/S690//P2.csv", row.names = FALSE)
```

# Extra plot, not needed
```{r}
library(VIM)
library(mice)
Practicum_2_aggr = aggr(P.2, col=mdc(1:2), numbers=TRUE, sortVars=TRUE, labels=names(P.2), cex.axis=.7, gap=1, ylab=c("Proportion of missingness","Missingness Pattern")) #check proportin of missingness and missing patterns, begin_weight has the most missing values
```